\chapter{INTRODUCTION}
  The report mainly  includes  the  drawbacks  of  the  previously  existing  system, Motivation, Problem  definition  of  the  project  and Scope of  the  project  etc. The Software Requirements Specifications (SRS) document defines the requirements for the system and the methods to be used to ensure that each requirement is satisfied for the project. This document encapsulates all  the  characteristics  and  features  expected  of  the  system  including  functionality,  user interfaces, performance and attributes. Any constraints to the implementation of the system are also discussed here. 

\section{Existing Sytem and Its Drawbacks}
\hspace{1cm}In the past video game industries were booming exponentially. But with the success rate of personal computers and mobile phones the online gaming websites and applications have become a hit. Earlier games were just for entertainment, to pass the time or to just relax the mind. But with the world being so competitive the cliché of entertainment in games has turned to learning. People tend to learn through games. People tend to learn in every moment. We believe in learning throughout the life. There are so many gaming applications which provide entertainment. But there are very few applications which provide knowledge through entertainment. This application is one among them.

 
\section{Motivation}
\hspace{1cm}The motivation for the “Mystery Doors” Windows project has two considerations. First one is the importance of logical reasoning and practical analysis. Second one  is  to  learn  building  the  applications  for  Windows  operating  system  which  will  be  the future extensive use in many mobile phones. Today, games have become a vital part in life. There is a huge competition between many mobile phone Operating Systems. To overcome this competition efficient and useful applications are necessary. Keeping this in mind we have developed this application for our windows OS users.\\

\section{Problem Statement}
\hspace{1cm}To develop an gaming application which will push the users intelligent level to its best. Different levels of puzzles are taken with interesting constraints imposed on the user. And will challenge the user to answer those questions to reach the final goal.\\

\section{Scope of project}	
\begin{itemize}
\item \textbf {}This mobile application is categorized under Games, where the main objective is entertainment. 
\item \textbf {}Entertainment is the main criteria of this application.
\item \textbf {}The main features of this application are- Entertainment, increasing the reasoning skills and it is suitable for all age groups.
\item \textbf {}The puzzle game instances that various players solve must be matched with the player ability.
\item \textbf {}The difficulty level must be maintained according to the player’s ability. We call this combined challenge as the “puzzle difficulty balance”.
\end{itemize}


